A Comparison of Graph Processing Systems

### 2020-09-01 documentation/paper/sections/graphFormats.tex
adjList to adjGraph with compressed sparse rows

The following sections explain the output formats of our conversion tool.
\subsubsection{AdjacencyList}
The AdjacencyList and WeightedAdjacencyList formats are used by Ligra and Polymer. The format was initially specified for the Problem Based Benchmark Suite, an open source repository to compare different parallel programming methodologies in terms of performance and code quality \cite{pbbs}.

@@

For the WeightedAdjacencyList format, the weights are appended to the end of the file in an order corresponding to the target nodes.

>>>>

The following sections explain the output formats of our conversion tool.
\subsubsection{AdjacencyGraph}
The AdjacencyGraph and WeightedAdjacencyGraph formats used by Ligra and Polymer are similar to the more popular \emph{compressed sparse rows} format.

The  The format was initially specified for the Problem Based Benchmark Suite, an open source repository to compare different parallel programming methodologies in terms of performance and code quality \cite{pbbs}.

@@

For the WeightedAdjacencyGraph format, the weights are appended to the end of the file in an order corresponding to the target nodes.

The files always start with the name of the format i.e. AdjacencyGraph or WeightedAdjacencyGraph in the first line.
